---
output: html_document
---

* Data loading and cleaning

The raw files are loaded and data cleaning drops the first 6 columns and the ones with NAs are dropped as well.

```{r}
submit <- read.csv("pml-testing.csv", na.strings=c("",NA))
dataset <- read.csv("pml-training.csv", na.strings=c("",NA))

dataset <- dataset[,-c(1:6)]
submit <- submit[,-c(1:6)]

dataset <- dataset[colSums(is.na(dataset)) == 0]
submit <- dataset[colSums(is.na(dataset)) == 0]
```

* Split into training/testing sets

The ratio is 60% for training and 40% for testing.

```{r}
library(caret)
inTrain <- createDataPartition(y=dataset$classe,
                               p=0.6, list=FALSE)

training <- dataset[inTrain,]
testing <- dataset[-inTrain,]
```

* Fitting model

The model used for prediction is random forest. The reason why the direct call to the randomForest is implemented and not using the caret is due to performance reasons - the caret's one was not finishing within a reasonable amount of time.

```{r}
library(randomForest)
modelFit <- randomForest(classe ~ ., data=training)
pred <- predict(modelFit,testing)

predTr <- predict(modelFit, training)
```

* Confusion Matrix

```{r}
confusionMatrix(data=pred, testing$classe)
```

* Out-of-sample error

Given that the accuracy of the model is 99.68% on the test set, the out-of-sample error is 0.32%
